---
title: "Practical Exam in CS101"
author: "Lore Faith Sabio BSIT-2B"
date: "2023-11-15"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
1. Load the mtcars.csv dataset into the R environment. Show your answer.
```{r 1}
data(mtcars)
head(mtcars)
```

2. How many observations does the mtcars have? How about the number of columns? List down the
names of the column. Show your answer.
```{r 2}
nrow(mtcars)
ncol(mtcars)
colnames(mtcars)
library(tibble)
head(mtcars)
mtcars <- rownames_to_column(mtcars,var = "models")
head(mtcars)
```
3. Generate a summary of the numerical variables as well as the structure of each variable in the mtcars
dataset. Show your solution
```{r 3}
summary(mtcars)
str(mtcars)
```
4. Create a bar chart to visualize the distribution of transmission types. Show your solution.
```{r 4}

```
5. Which from the model has the highest mpg? How about the car model with the highest horsepower?
Show your solution that will display the name of the model with the highest mpg and the car model
with the highest horsepower

```{r 5}
max_mpg <- mtcars[which.max(mtcars$mpg), ]

max_hp<- mtcars[which.max(mtcars$hp), ]

cat("Car model with the highest mpg:", max_mpg$models, "\n")
cat("Car model with the highest horsepower:", max_hp$models, "\n")
```
6. Which from the car models having 8 cylinders? Save this as newCar.csv file. Display the 1st two rows
of this dataset. Show your solution.
```{r 6}
eightCyl <- mtcars[mtcars$cyl == 8, ]
write.csv(eightCyl, file = "newCar.csv", row.names = FALSE)
head(eightCyl, 2)
```

7. Calculate the mean mpg of the car models with 6 cylinders. Show your solution.
```{r 7}
meanMpg <- mean(mtcars$mpg[mtcars$cyl == 6])

cat("Mean mpg for car models with 6 cylinders:", meanMpg, "\n")
```
